### 2019-07-08 README.rmd
updates and renders README

<!-- Code status -->
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean)

@@

```{r}
my.code <- clean("./example/simple_script.R", "tab.15")
write.code(my.code, file = "x.R")
```

@@

```{r}
write.code(my.code)
```

>>>>

<!-- Code status -->
[![Dev: Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean) 
[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/dev/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=dev)

@@

```{r eval = FALSE}
my.code <- clean("./example/simple_script.R", "tab.15")
write.code(my.code, file = "x.R")
```

@@

```{r eval = FALSE}
write.code(my.code)
```
